Digital Humanities - Ashoka University

### 2021-10-14 Submission.Rmd
.

```{r load_data_libraries, include=FALSE}
load("saved_data.rda")
load("saved_ner.rda")
library(knitr)
```
### Understanding Emotion in Hemingway's and Fitzgerald's work

>>>>

```{r load_data_libraries, include=FALSE}
load("saved_data.rda")
load("saved_ner.rda")
library(knitr)
```
### Throwing Fitz in E(a)rnest: An Analysis of Emotion in Fitzgerald and Hemingway
